---
title: "Visualization"
subtitle: "Part 1"
output: github_document
---

```{r setup}
library(tidyverse)
library(ggridges)
```

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728", "USC00519397", "USS0023B17S"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(
      id, 
      USW00094728 = "CentralPark_NY", 
      USC00519397 = "Waikiki_HA",
      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())

weather_df
```

## Scatterplots!

Creating my very first scatterplot.

```{r}
ggplot(weather_df, aes(x = tmin, y = tmax)) +
  geom_point()
```

New approach, same plot.

```{r}
weather_df %>% 
# Can do filter here, benefit to using piping
  ggplot(aes(x = tmin, y = tmax)) +
  geom_point()
```

Save and edit a plot object.

```{r}
weather_plot = 
  weather_df %>% 
  ggplot(aes(x = tmin, y = tmax))

weather_plot + geom_point()
```

## Advanced scatterplot ...

Start with the same one and make it fancy!

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, color = name)) +
  geom_point() +
  geom_smooth(se = FALSE)
```

What about the aes placement ... ?

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax)) +
  geom_point(aes(color = name)) +
  geom_smooth()
```

In above code, because color was defined only for the points, geom smooth applied one line.

Let's facet some things!

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, color = name)) +
  geom_point(alpha = 0.2, size = 0.3) +
  geom_smooth(se = FALSE, size = 0.5) +
  facet_grid(. ~ name)
```

Can also have alpha = tmin to create transparency towards lower values of tmin and less transparency towards higher values of tmin.

Let's combine some elements are try a new plot.

```{r}
weather_df %>% 
  ggplot(aes(x = date, y = tmax, color = name)) +
  geom_point(aes(size = prcp), alpha = 0.5) + 
  geom_smooth(se = FALSE) +
  facet_grid(. ~ name)
```

## Some small notes

How many geoms have to exist?

You can have whatever geoms you want.

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, color = name)) +
  geom_smooth(se = FALSE)
```

You can use a neat geom!

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax)) +
  geom_hex()
```

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax)) +
  geom_density2d() + 
  geom_point(alpha = 0.3)
```

## Univariate plots

Histograms are really great. 

```{r}
weather_df %>% 
  ggplot(aes(x = tmin)) +
  geom_histogram()
```

Can we add color ... ?

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, fill = name)) +
  geom_histogram() + 
  facet_grid(. ~ name)
```

Let's try a new geometry!

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, fill = name)) +
  geom_density(alpha = 0.4, adjust = 0.5)
```

What about boxplots??

```{r}
weather_df %>% 
  ggplot(aes(x = name, y = tmin)) +
  geom_boxplot()
```

Trendy plots!

```{r}
weather_df %>% 
  ggplot(aes(x = name, y = tmin, fill = name)) + 
  geom_violin(alpha = 0.5) +
  stat_summary(fun = "median")
```

Ridge plots -- the most popular plot of 2017.

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = name)) +
  geom_density_ridges()
```







