---
title: "Data Import"
output: github_document
---

```{r setup}
library(tidyverse)
library(readxl)
library(haven)
```

## Read in some data

Read in the litters dataset.

```{r}
litters_df = read_csv("./data/FAS_litters.csv")
litters_df = janitor::clean_names(litters_df)
```

## Take a look at the data

Printing in the console.

```{r}
litters_df
```

```{r}
tail(litters_df)
skimr::skim(litters_df)
```

## Options to read CSV

Check out `?read_csv` for more information.

```{r}
litters_df = read_csv("./data/FAS_litters.csv", 
                      skip = 10, 
                      col_names = FALSE, 
                      na = c("", 99, "NA"))
```

## Other file formats

Let's read in an Excel file.
Better to load entire package for the readxl case, as sometimes there are helper functions working in the background.

```{r}
mlb_df = read_excel("./data/mlb11.xlsx", range = "A1:F7")
```

Read in a SAS file.

```{r}
pulse_df = read_sas("./data/public_pulse_data.sas7bdat")
```

## Comparison with Base R

What about `read.csv` ... ? Never use. Base R version is more difficult to look at.

```{r}
litters_base = read.csv("./data/FAS_litters.csv")
litters_readr = read_csv("./data/FAS_litters.csv")
```

## Exporting data

Export the mlb sub-table.

```{r}
write_csv(mlb_df, "./data/mlb_sub.csv")
```



